Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2019-07-12 awipev-CO2.Rmd
Uncommented the poster sections

# #plot for POSTER june 2019
# #plot of S/T
# poster_temp <- ggplot(data = d_all%>%dplyr::filter(temp_fb<10 &sal_fb>30 )) + geom_point(aes(x=datetime,y=temp_fb),col="blue", size=0.5) +
#   geom_point(aes(x=datetime,y=sal_fb/5),col="red", size=0.5 )+
#   labs(x = "Time", y="Temperature (°C)") +
#   scale_x_datetime(date_minor_breaks ="1 month")+
#   theme_bw() + theme(legend.position="bottom",legend.title = element_blank())+
#   scale_y_continuous(sec.axis = sec_axis(~.*5, name = "Salinity"))
# print(poster_temp)
# 
# png("figures/poster_sal_temp.png", width= 1100, height=600)
# par(mar=c(5, 4, 4, 6) + 0.1)
# 
# plot(sal_fb ~ datetime,d_all,pch=16, axes=T, ylim=c(30.5,36), cex=0.5, col="red", ylab="", xlab="", yaxt ="n", lty=1, cex.axis=1.8) +
# axis(2, ylim=c(0,1),col="red",col.axis="red", las = 1,lty=1, cex.axis =1.8)
# 
#     grid(lty=1)
# 
#    par(new = T)
# 
# plot(as.Date(d_all$datetime,"%Y-%m-d %H:%M:%S", tz= "UTC"), d_all$temp_fb, col="blue", pch=16, cex=0.5, xlab="", ylab="",xaxt="n", axes=FALSE,ylim=c(-2,9))+
# axis(side = 4, col="blue",col.axis="blue",las=1, cex.axis =1.8) +
# mtext("",side=1,col="black",line=1.5, cex=1.8)
# legend("topleft", legend=c("Temperature (°C)", "Salinity"),
#        col = c("blue", "red"), pch  = c(16, 16),  box.lty=0 , cex = 2)
#   #grid(nx = 1, ny = NULL, col = "lightgray", lty = 1,
#    #  lwd = "months")
#      box()
#      dev.off()

# ggsave(paste0("figures/poster_temp.png"), width= 30, height=10, poster_temp, units="cm")
# 
# poster_sal <- ggplot(data = d_all%>%dplyr::filter(sal_fb>30 ), aes(x=datetime,y=sal_fb), colour="sal_fb") +
#   geom_point(col="blue", size=0.5 )+
#   labs(x = "Time", y="Salinity (PSU)") +
#   scale_x_datetime(date_minor_breaks ="1 month")+
#   theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
# print(poster_sal)
# ggsave(paste0("figures/poster_sal.png"), width= 30, height=10, poster_sal, units="cm")

@@

# #plot for POSTER june 2019
# #plot of TA calculated from S + discrete
# p_at_sal <- ggplot(data = d_all%>%dplyr::filter(at_calc > 2000), aes(x=datetime,y=at_calc,col="TA calculated from salinity") ) +
#   geom_point(col="blue", size=0.5 )+
#   geom_point(aes(y=at, fill= "Discrete measurements"), col="red") +
#   labs(title=  "Calculated from salinity (µmol/kg)", x = "", y= "") + ylim(2100,2350)+
#   theme_bw() + scale_x_datetime(minor_breaks  = "1 month ")+
#   theme(legend.position= c(0.5, 0.93),
#                      legend.text=element_text(size=15),
#                      plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin(t = 9, b = -25)),
#                      axis.text=element_text(size=15),
#                      axis.title.x= element_text(size =15),
#                      legend.title=element_blank())
# 
# 
# print(p_at_sal)
# ggsave(paste0("figures/poster_at_sal.png"), width= 30, height=10, p_at_sal, units="cm")

@@

# #plot for POSTER june 2019
# #plot of pCO2
# 
# #  add pCO2 atmospheric data from URL
# 
# noaa <- read.csv("pco2_noaa.txt", header=T, sep ="", dec=".", stringsAsFactors = FALSE)
# noaa <- noaa %>%
#   dplyr::select(sample_year, sample_month, sample_day, sample_hour, sample_minute, sample_seconds, analysis_value, analysis_uncertainty) %>%
#   unite("date", c("sample_year", "sample_month", "sample_day"), sep="-")%>%
#   unite("time", c("sample_hour", "sample_minute", "sample_seconds"), sep=":") %>%
#   unite("datetime", c("date", "time"), sep=" ")
# 
# noaa$datetime <- ymd_hms(noaa$datetime, tz="UTC")
# noaa <- noaa %>%
#  dplyr::filter(datetime > "2015-07-01 00:00:00")
# 
# #create a lab expression for pCO2 NOAA data lebel. Include it with scale_shape_discrete(labels=lab)
# lab <- c( expression(paste(italic(p),CO[2]," (µatm)")),
#           expression(paste(italic(p),CO[2]," (ppm; from NOAA)")),
#            "Calculated from AT/CT"
#           
#           )
# 
# col <- c("blue","black","red")
# 
# poster_pco2 <- ggplot( ) +
#   geom_point(data=d_all%>%dplyr::filter(pco2_contros > 150 & pco2_contros < 410), aes(x=datetime, y= pco2_contros, shape ="lab", colour="blue"),size=0.5 ) +
#   geom_point(data=d_all, aes(x=datetime, y=pco2calc, shape="lab" , color= "red"))+
#   geom_point() + geom_point(data=noaa%>%dplyr::filter(analysis_value > 150), aes(x=datetime, y= analysis_value, shape="lab", color ="col" ),size=0.5)+
#   scale_shape_discrete(labels=lab, guide="none")+
#   scale_colour_manual(labels=lab, values=col)+
#   labs(x = "", y ="", title = "") +
#   theme_bw() +
#   scale_x_datetime(minor_breaks  = "1 month ")+
#   theme(legend.position="top",  #c(0.18, 0.85)
#                      legend.text=element_text(size=14, colour="black"),
#                      #plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -30)),
#                      axis.text=element_text(size=15),
#                      plot.margin = unit(c(0.5,1,1,1), "cm"),
#                      axis.title.x= element_text(size =15),
#                      legend.title=element_blank()
#                      ) 
# print(poster_pco2)
#   ggsave(paste0("figures/poster_pco2.png"), width= 30, height=10, poster_pco2, units="cm")

@@

# #plot for POSTER june 2019
# #plot of pH seafet
# poster_ph <- ggplot( ) +
#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= pHint_tot_sf,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_seafet_temp_field, fill="Discrete measurements"), col="red" )+
#   labs(x = "", y ="", title = expression(pH[T]~seaFET)) +
#   theme_bw() + scale_x_datetime(minor_breaks  = "1 month ")+
#   theme(legend.position= c(0.17, 0.8),
#                      legend.text=element_text(size=14),
#                       plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -35)),
#                       axis.text=element_text(size=15),
#                       plot.margin = unit(c(1,1,1,1), "cm"),
#                       axis.title.x= element_text(size =15),
#                       legend.title=element_blank())
# 
# print(poster_ph)
# ggsave(paste0("figures/poster_ph.png"), width= 30, height=10, poster_ph, units="cm")

# # RANGE of pH
# d_all<- d_all%>%
#   dplyr::mutate(year = year(datetime))
# range <- tbl_df(
#   d_all %>%
#   group_by(date=as.Date(datetime), month=month(datetime, label=TRUE), year=year(datetime)) %>%
#   summarize(pH_range = max(pHint_tot_sf) - min(pHint_tot_sf))
# )
# quant <- quantile(range$pH_range, probs =c(2.5/100, 97.5/100), na.rm =TRUE)
# 
# # Per month
# range_month <-
#   range %>%
#   group_by(Month = month(date, label=TRUE, abbr=FALSE)) %>%
#   summarize(pH_range_month = mean(pH_range, na.rm=TRUE))
# 
# size_point <- 0.4 # size of data points
# plot_range_sf <-  
#   ggplot(data=range, aes(x = as.factor(month), y = pH_range)) +
#   geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
#   geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
#   labs(y =expression(paste(pH[T], " range seaFET")), x=NULL, title=NULL) +
#   Mytheme() +
#   theme(panel.grid.major.x = element_blank())
# print(plot_range_sf)
# ggsave(paste0("figures/plot_range_sf.png"), width= 30, height=10, plot_range_sf, units="cm")

@@

# #plot for POSTER june 2019
# #plot of pH durafet
#  poster_dur <- ggplot( ) +
#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= pH_durafet_corrected,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_durafet_temp_field, fill="Discrete measurements"), col="red" )+
#   labs(x = "", y= "", title = expression(pH[T]~durafet)) +
#   theme_bw() + scale_x_datetime(minor_breaks  = "1 month ")+
#    theme(legend.position= c(0.17, 0.8),
#                      legend.text=element_text(size=14),
#                       plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -35)),
#                       axis.text=element_text(size=15),
#                       plot.margin = unit(c(1,1,1,1), "cm"),
#                       axis.title.x= element_text(size =15),
#                       legend.title=element_blank())
# 
# print(poster_dur)
# ggsave(paste0("figures/poster_dur.png"), width= 30, height=10, poster_dur, units="cm")
# 
# # RANGE of pH
# range_dur <- tbl_df(
#   d_all %>%
#   group_by(date=as.Date(datetime), month=month(datetime, label=TRUE), year=year(datetime)) %>%
#   summarize(pH_range = max(pH_durafet_corrected) - min(pH_durafet_corrected))
# )
# quant <- quantile(range_dur$pH_range, probs =c(2.5/100, 97.5/100), na.rm =TRUE)
# 
# # Per month
# range_month <-
#   range_dur %>%
#   group_by(Month = month(date, label=TRUE, abbr=FALSE)) %>%
#   summarize(pH_range_month = mean(pH_range, na.rm=TRUE))
# 
# size_point <- 0.4 # size of data points
# plot_range_dur <-  
#   ggplot(data=range_dur, aes(x = as.factor(month), y = pH_range)) +
#   geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
#   geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
#   labs(y =expression(paste(pH[T], " range durafet")), x=NULL, title=NULL) +
#   Mytheme() +
#   theme(panel.grid.major.x = element_blank())
# print(plot_range_dur)
# ggsave(paste0("figures/plot_range_dur.png"), width= 30, height=10, plot_range_dur, units="cm")
```
The average offset between durafet and references (spectro) data is `r average_offset_dur` pH unit (sd = `r sd_offset_dur`, n = `r n_offset_dur`).

>>>>

#plot for POSTER june 2019
#plot of S/T
poster_temp <- ggplot(data = d_all%>%dplyr::filter(temp_fb<10 &sal_fb>30 )) + geom_point(aes(x=datetime,y=temp_fb),col="blue", size=0.5) +
  geom_point(aes(x=datetime,y=sal_fb/5),col="red", size=0.5 )+
  labs(x = "Time", y="Temperature (°C)") +
  scale_x_datetime(date_minor_breaks ="1 month")+
  theme_bw() + theme(legend.position="bottom",legend.title = element_blank())+
  scale_y_continuous(sec.axis = sec_axis(~.*5, name = "Salinity"))
print(poster_temp)
#
png("figures/poster_sal_temp.png", width= 1100, height=600)
par(mar=c(5, 4, 4, 6) + 0.1)
#
plot(sal_fb ~ datetime,d_all,pch=16, axes=T, ylim=c(30.5,36), cex=0.5, col="red", ylab="", xlab="", yaxt ="n", lty=1, cex.axis=1.8) +
axis(2, ylim=c(0,1),col="red",col.axis="red", las = 1,lty=1, cex.axis =1.8)
#
   grid(lty=1)
#
   par(new = T)
#
plot(as.Date(d_all$datetime,"%Y-%m-d %H:%M:%S", tz= "UTC"), d_all$temp_fb, col="blue", pch=16, cex=0.5, xlab="", ylab="",xaxt="n", axes=FALSE,ylim=c(-2,9))+
axis(side = 4, col="blue",col.axis="blue",las=1, cex.axis =1.8) +
mtext("",side=1,col="black",line=1.5, cex=1.8)
legend("topleft", legend=c("Temperature (°C)", "Salinity"),
       col = c("blue", "red"), pch  = c(16, 16),  box.lty=0 , cex = 2)
  grid(nx = 1, ny = NULL, col = "lightgray", lty = 1,
    lwd = "months")
     box()
     dev.off()

ggsave(paste0("figures/poster_temp.png"), width= 30, height=10, poster_temp, units="cm")
#
poster_sal <- ggplot(data = d_all%>%dplyr::filter(sal_fb>30 ), aes(x=datetime,y=sal_fb), colour="sal_fb") +
  geom_point(col="blue", size=0.5 )+
  labs(x = "Time", y="Salinity (PSU)") +
  scale_x_datetime(date_minor_breaks ="1 month")+
  theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
print(poster_sal)
ggsave(paste0("figures/poster_sal.png"), width= 30, height=10, poster_sal, units="cm")

@@

#plot for POSTER june 2019
#plot of TA calculated from S + discrete
p_at_sal <- ggplot(data = d_all%>%dplyr::filter(at_calc > 2000), aes(x=datetime,y=at_calc,col="TA calculated from salinity") ) +
  geom_point(col="blue", size=0.5 )+
  geom_point(aes(y=at, fill= "Discrete measurements"), col="red") +
  labs(title=  "Calculated from salinity (µmol/kg)", x = "", y= "") + ylim(2100,2350)+
  theme_bw() + scale_x_datetime(minor_breaks  = "1 month ")+
  theme(legend.position= c(0.5, 0.93),
                     legend.text=element_text(size=15),
                     plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin(t = 9, b = -25)),
                     axis.text=element_text(size=15),
                     axis.title.x= element_text(size =15),
                     legend.title=element_blank())

print(p_at_sal)
ggsave(paste0("figures/poster_at_sal.png"), width= 30, height=10, p_at_sal, units="cm")

@@

#plot for POSTER june 2019
#plot of pCO2

#  add pCO2 atmospheric data from URL

noaa <- read.csv("pco2_noaa.txt", header=T, sep ="", dec=".", stringsAsFactors = FALSE)
noaa <- noaa %>%
  dplyr::select(sample_year, sample_month, sample_day, sample_hour, sample_minute, sample_seconds, analysis_value, analysis_uncertainty) %>%
  unite("date", c("sample_year", "sample_month", "sample_day"), sep="-")%>%
  unite("time", c("sample_hour", "sample_minute", "sample_seconds"), sep=":") %>%
  unite("datetime", c("date", "time"), sep=" ")

noaa$datetime <- ymd_hms(noaa$datetime, tz="UTC")
noaa <- noaa %>%
 dplyr::filter(datetime > "2015-07-01 00:00:00")

#create a lab expression for pCO2 NOAA data lebel. Include it with scale_shape_discrete(labels=lab)
lab <- c( expression(paste(italic(p),CO[2]," (µatm)")),
          expression(paste(italic(p),CO[2]," (ppm; from NOAA)")),
           "Calculated from AT/CT"

          )

col <- c("blue","black","red")

poster_pco2 <- ggplot( ) +
  geom_point(data=d_all%>%dplyr::filter(pco2_contros > 150 & pco2_contros < 410), aes(x=datetime, y= pco2_contros, shape ="lab", colour="blue"),size=0.5 ) +
  geom_point(data=d_all, aes(x=datetime, y=pco2calc, shape="lab" , color= "red"))+
  geom_point() + geom_point(data=noaa%>%dplyr::filter(analysis_value > 150), aes(x=datetime, y= analysis_value, shape="lab", color ="col" ),size=0.5)+
  scale_shape_discrete(labels=lab, guide="none")+
  scale_colour_manual(labels=lab, values=col)+
  labs(x = "", y ="", title = "") +
  theme_bw() +
  scale_x_datetime(minor_breaks  = "1 month ")+
  theme(legend.position="top",  #c(0.18, 0.85)
                     legend.text=element_text(size=14, colour="black"),
                     #plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -30)),
                     axis.text=element_text(size=15),
                     plot.margin = unit(c(0.5,1,1,1), "cm"),
                     axis.title.x= element_text(size =15),
                     legend.title=element_blank()
                     )
print(poster_pco2)
  ggsave(paste0("figures/poster_pco2.png"), width= 30, height=10, poster_pco2, units="cm")

@@

#plot for POSTER june 2019
#plot of pH seafet
poster_ph <- ggplot() +
  geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= pHint_tot_sf,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
  geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_seafet_temp_field, fill="Discrete measurements"), col="red" )+
  labs(x = "", y ="", title = expression(pH[T]~seaFET)) +
  theme_bw() + scale_x_datetime(minor_breaks  = "1 month ")+
  theme(legend.position= c(0.17, 0.8),
                     legend.text=element_text(size=14),
                      plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -35)),
                      axis.text=element_text(size=15),
                      plot.margin = unit(c(1,1,1,1), "cm"),
                      axis.title.x= element_text(size =15),
                      legend.title=element_blank())

print(poster_ph)
ggsave(paste0("figures/poster_ph.png"), width= 30, height=10, poster_ph, units="cm")

#RANGE of pH
d_all<- d_all%>%
  dplyr::mutate(year = year(datetime))
range <- tbl_df(
  d_all %>%
  group_by(date=as.Date(datetime), month=month(datetime, label=TRUE), year=year(datetime)) %>%
  summarize(pH_range = max(pHint_tot_sf) - min(pHint_tot_sf))
)
quant <- quantile(range$pH_range, probs =c(2.5/100, 97.5/100), na.rm =TRUE)

#Per month
range_month <-
  range %>%
  group_by(Month = month(date, label=TRUE, abbr=FALSE)) %>%
  summarize(pH_range_month = mean(pH_range, na.rm=TRUE))

size_point <- 0.4 #size of data points
plot_range_sf <-  
  ggplot(data=range, aes(x = as.factor(month), y = pH_range)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  labs(y =expression(paste(pH[T], " range seaFET")), x=NULL, title=NULL) +
  Mytheme() +
  theme(panel.grid.major.x = element_blank())
print(plot_range_sf)
ggsave(paste0("figures/plot_range_sf.png"), width= 30, height=10, plot_range_sf, units="cm")

@@

#plot for POSTER june 2019
#plot of pH durafet
 poster_dur <- ggplot( ) +
  geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= pH_durafet_corrected,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
  geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_durafet_temp_field, fill="Discrete measurements"), col="red" )+
  labs(x = "", y= "", title = expression(pH[T]~durafet)) +
  theme_bw() + scale_x_datetime(minor_breaks  = "1 month ")+
   theme(legend.position= c(0.17, 0.8),
                     legend.text=element_text(size=14),
                      plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -35)),
                      axis.text=element_text(size=15),
                      plot.margin = unit(c(1,1,1,1), "cm"),
                      axis.title.x= element_text(size =15),
                      legend.title=element_blank())

print(poster_dur)
ggsave(paste0("figures/poster_dur.png"), width= 30, height=10, poster_dur, units="cm")

# RANGE of pH
range_dur <- tbl_df(
  d_all %>%
  group_by(date=as.Date(datetime), month=month(datetime, label=TRUE), year=year(datetime)) %>%
  summarize(pH_range = max(pH_durafet_corrected) - min(pH_durafet_corrected))
)
quant <- quantile(range_dur$pH_range, probs =c(2.5/100, 97.5/100), na.rm =TRUE)

# Per month
range_month <-
  range_dur %>%
  group_by(Month = month(date, label=TRUE, abbr=FALSE)) %>%
  summarize(pH_range_month = mean(pH_range, na.rm=TRUE))

size_point <- 0.4 # size of data points
plot_range_dur <-
  ggplot(data=range_dur, aes(x = as.factor(month), y = pH_range)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  labs(y =expression(paste(pH[T], " range durafet")), x=NULL, title=NULL) +
  Mytheme() +
  theme(panel.grid.major.x = element_blank())
print(plot_range_dur)
ggsave(paste0("figures/plot_range_dur.png"), width= 30, height=10, plot_range_dur, units="cm")
```
The average offset between durafet and references (spectro) data is `r average_offset_dur` pH unit (sd = `r sd_offset_dur`, n = `r n_offset_dur`).
